---
title: "R markdown"
author: ".."
date: "11/25/2021"
output: html_document
---

```{r}
library(haven)
data<-read_dta("C:/Users/Admin/Downloads/440136784_trc_data_3411635738307577.dta")
head(data)
```

Question 3a)

```{r}
set.seed(210)
library(tidyverse)
library(cowplot)
n <- 1000 # some population with 1000 observations
epsilon <- rnorm(n,mean=0,sd=1) # just a simple random error which we don't observe
X_underlying <- runif(n,min=-1,max=1)
X <- ifelse(X_underlying>0, 1, 0) # X is something super simple, an indicator variable which is 1 if X_underlying is positive and 0 otherwise
A <- runif(n,min=5,max=6) # A is also something super simple, a uniform random variable living in [5,6]

Y <- 1 + 5*X - A + epsilon # Y is a simple linear function of X and A

dataset <- data.frame(Y=Y, X=X, A=A) # Let's put this together in a dataframe. We don't include epsilon since it's an unobserved random error term.
```

```{r}
E_Y_X_1 <- dataset %>% filter(X==1) %>% summarise(conditional_mean = mean(Y))
E_Y_X_0 <- dataset %>% filter(X==0) %>% summarise(conditional_mean = mean(Y))
ATE_filter <- E_Y_X_1 - E_Y_X_0
names(ATE_filter) <- c("ATE_filter")
ATE_filter
```

```{r}
t.test(dataset$Y[X==1], dataset$Y[X==0])
```

## Part b)

The exposed respondents and unexposed respondents differ significantly by value of their parameters the respondents are good predictors an have a significant p-value as compared to the exposed respondents.This is caused by the nature in which they occur.

## Par c)
```{r}
library(twang)
data(iptwExWide)
iptw.Ex <- iptw(list(tx1 ~ use0 + gender + age,
 tx2 ~ use1 + use0 + tx1 + gender + age,
 tx3 ~ use2 + use1 + use0 + tx2 + tx1 + gender + age),
 timeInvariant ~ gender + age,
 data = iptwExWide,
 cumulative = FALSE,
 priorTreatment = FALSE,
 verbose = FALSE,
 stop.method = "es.max",
 n.trees = 5000)
```

```{r}
plot(iptw.Ex, plots = 1)
```

## Part d

```{r}
unstabWt1 <- get.weights.unstab(iptw.Ex)
 library(survey)
 nTx <- with(iptwExWide, tx1 + tx2 + tx3)
 outDatUnstab <- data.frame(outcome = iptwExWide$outcome,
 nTx,
 wt = unstabWt1$es.max.ATE)
 sv1unstab <- svydesign(~1, weights = ~wt, data = outDatUnstab)
 fitUnstab <- svyglm(outcome ~ nTx, sv1unstab)
 coef(fitUnstab)
confint(fitUnstab)
```
Since our data trc_data it is observed that the true treatment effect is -0.987.It is observed that the true treatment efectcovers the pronspensity score-weighted estimates cover.

For the sake of extracting valid comparisons we investigate the we will then report the estimate and the corresponding confidence interval

```{r}
fitList <- list(glm(tx1 ~ 1, family = binomial, data = iptwExWide),
glm(tx2 ~ tx1, family = binomial, data = iptwExWide),
glm(tx3 ~ tx1 + tx2, family = binomial, data = iptwExWide))
numWt <- get.weights.num(iptw.Ex, fitList)
stabWt1 <- unstabWt1 * numWt

outDatStab <- data.frame(outcome = iptwExWide$outcome,
nTx,
wt = stabWt1$es.max.ATE)
sv1stab <- svydesign(~1, weights = ~wt, data = outDatStab)
fitStab <- svyglm(outcome ~ nTx, sv1stab)
confint(fitStab)
```

## Question 4 

### Part a)

```{r}
library(Matching)
 #NOT RUN {
# Replication of Dehejia and Wahba psid3 model
#
# Dehejia, Rajeev and Sadek Wahba. 1999.``Causal Effects in
# Non-Experimental Studies: Re-Evaluating the Evaluation of Training
# Programs.''Journal of the American Statistical Association 94 (448):
# 1053-1062.

data(lalonde)

#
# Estimate the propensity model
#
glm1  <- glm(treat~age + I(age^2) + educ + I(educ^2) + black +
             hisp + married + nodegr + re74  + I(re74^2) + re75 + I(re75^2) +
             u74 + u75, family=binomial, data=lalonde)


#
#save data objects
#
X  <- glm1$fitted
Y  <- lalonde$re78
Tr  <- lalonde$treat

#
# one-to-one matching with replacement (the "M=1" option).
# Estimating the treatment effect on the treated (the "estimand" option defaults to ATT).
#
rr  <- Match(Y=Y, Tr=Tr, X=X, M=1);
summary(rr)

# Let's check the covariate balance
# 'nboots' is set to small values in the interest of speed.
# Please increase to at least 500 each for publication quality p-values.
mb  <- MatchBalance(treat~age + I(age^2) + educ + I(educ^2) + black +
                    hisp + married + nodegr + re74  + I(re74^2) + re75 + I(re75^2) +
                    u74 + u75, data=lalonde, match.out=rr, nboots=10)
# }
```

## Part b

```{r}
summary(glm1)
```
## Part C

```{r}
summary(sv1stab)
```

There was no increase in standard error change of the above model.

## Part d

```{r}
data(mnIptwExWide)
 mniptw.Ex <- iptw(list(tx1 ~ use0, tx2 ~ use1, tx3 ~ use2),
timeInvariant ~ gender + age,
data = mnIptwExWide,

cumulative = TRUE,
riorTreatment = TRUE,
verbose = FALSE,
stop.method = "es.max",
n.trees = 5000)
```

```{r}
summary(mniptw.Ex)
```
